### 2024-07-22 NN/tables/backward.tex
commit

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                           &    R2 \\
\hline
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
 ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 88.38 \\
 ['flow_rate1', 'conc_nano1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']    & 58.85 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 67.6  \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2'] & 82.77 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 57.26 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 74.21 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']    & 55.88 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']       & 64.76 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2'] & 73.37 \\
 ['Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.52 \\
 ['flow_rate1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                  & 67.85 \\
 ['flow_rate1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 81.99 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']               & 74.67 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.17 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 16.53 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']                  & 74.26 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']                     & 66.81 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2']               & 69.09 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}

>>>>

        \begin{table*}
            \centering
            \begin{tabular}{lr}
\hline
 features                                                                                                           &    R2 \\
\hline
 ['flow\_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 76.09 \\
 ['conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 43.37 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 88.38 \\
 ['flow_rate1', 'conc_nano1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']    & 58.85 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 67.6  \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2'] & 82.77 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 57.26 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']       & 74.21 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']    & 55.88 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']       & 64.76 \\
 ['flow_rate1', 'conc_nano1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2'] & 73.37 \\
 ['Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.52 \\
 ['flow_rate1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                  & 67.85 \\
 ['flow_rate1', 'Kfluid1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 81.99 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']               & 74.67 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'conc_nano2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 83.17 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'Kfluid2', 'heat_flux2', 'X_D2']                     & 16.53 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'heat_flux2', 'X_D2']                  & 74.26 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'X_D2']                     & 66.81 \\
 ['flow_rate1', 'Kfluid1', 'heat_flux1', 'X_D1', 'flow_rate2', 'conc_nano2', 'Kfluid2', 'heat_flux2']               & 69.09 \\
\hline
\end{tabular}
            \caption{Results of Backward Feature Elimination}
            \label{table-backward}
        \end{table*}
